Keyphrase Extraction from User Generated Contents on Medical Domain

### 2017-05-24 paper.tex
nambahin footnote Konsil

\textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary. The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from \cite{skripsiKakAbid} research. The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug. Based on this feature, we classified words by their appearance in the medical dictionary. We represent this feature as one-hot-vector.

>>>>

\textbf{Medical Dictionary (Md).} In our experiment, we leverage a medical knowledge base feature using a medical dictionary. The dictionary was built by combining disease, symptom, treatment, and drug dictionaries from Konsil Kedokteran Indonesia\footnote{www.
kki.go.id/assets/data/arsip/SKDI_Perkonsil,_11_maret_13.pdf.}. The rationale behind this feature is intentions and needs of patients is more focused on their disease, symptom, treatment, and drug. Based on this feature, we classified words by their appearance in the medical dictionary. We represent this feature as one-hot-vector.
